Finding Subgraphs With Side Constraints\thanks{This research was supported by the Engineering and Physical Sciences Research Council [grant number EP/P026842/1]}

### 2021-01-21 paper/paper.tex
Abstract

\begin{abstract}
    The subgraph isomorphism problem is to find a small ``pattern'' graph inside a larger ``target''
    graph. There are excellent dedicated solvers for this problem, but they require substantial
    programming effort to handle complex side constraints; however, general purpose constraint
    solvers struggle on more difficult graph instances. We show how to combine the state of the art
    Glasgow Subgraph Solver with the Minion constraint programming solver to get a ``subgraphs modulo
    theories'' solver that is both performant and flexible. We also show how such an approach can be
    driven by the Essence high level modelling language. We give practical examples taken from
    ??applications.
\end{abstract}

>>>>

\begin{abstract}
    The subgraph isomorphism problem is to find a small ``pattern'' graph inside a larger ``target''
    graph. There are excellent dedicated solvers for this problem, but they require substantial
    programming effort to handle complex side constraints; however, general purpose constraint
    solvers struggle on more difficult graph instances. We show how to combine the state of the art
    Glasgow Subgraph Solver with the Minion constraint programming solver to get a ``subgraphs modulo
    theories'' solver that is both performant and flexible. We also show how such an approach can be
    driven by the Essence high level modelling language, giving ease of modelling to non-expert
    users. We give practical examples involving
    temporal graphs, typed graphs from software engineering, and costed subgraph isomorphism
    problems.
\end{abstract}
